Draft: Notes on the revised Hidden weight function

### 2024-10-08 RevisedHiddenWeight.tex
Proofs for generalizations (with parameter t)

As a consequence, we have:

@@

In particular, $d_{n,n}(x)=d_n(x)$.

@@

\begin{proposition}\label{proposition:dtn}
	Let $t, n\in \N$ with $n$ even and $t\le n/2$, the following holds on $d_{t,n}$ for all $k\in [0,n]$:
	\[\wtk{d_{t,n}}{k}(a)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t},\]
	where $b$ denotes the first $2t$ elements of $a$ and $c$ the last $n-2t$ elements.

\end{proposition}
\begin{proof}
	We rewrite the restricted Walsh transform, denoting $x\in \F_2^n$ by $(y,z)$ where $y\in \F_2^{2t}$ and $z \in \F_2^{n-2t}$, and similarly denoting $a$ by $(b,c)$:

	\begin{align*}
	\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,t}(y)+by +cz}\\
	&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,t}(y)+by +cz}\\
	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,t}(y)+by} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{cz}\right)\\
	&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
	\end{align*}

\end{proof}

>>>>

@@

In particular, $d_{n/2,n}(x)=d_n(x)$.

@@

\begin{proposition}\label{proposition:dtn}
	Let $t, n\in \N$ with $n$ even and $t\le n/2$, the following holds on $d_{t,n}$ for all $k\in [0,n]$:
	\[\wtk{d_{t,n}}{k}(a)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t},\]
	where $b$ denotes the first $2t$ elements of $a$ and $c$ the last $n-2t$ elements.
\end{proposition}
\begin{proof}
	We rewrite the restricted Walsh transform, denoting $x\in \F_2^n$ by $(y,z)$ where $y\in \F_2^{2t}$ and $z \in \F_2^{n-2t}$, and similarly denoting $a$ by $(b,c)$:

	\begin{align*}
	\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,t}(y)+by +cz}\\
	&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,t}(y)+by +cz}\\
	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,t}(y)+by} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{cz}\right)\\
	&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
	\end{align*}	
\end{proof}

This leads to the following generating function:

\begin{proposition}
    Let $t, n\in \N$ with $n$ even and $t\le n/2$. Let $a=(b,c)\in\F_2^n$ with $b\in\F_2^{2t}$. Denote $n-2t-\w(c)$ and $\w(c)$ by $u$ and $v$, respectively. Then the following holds:
    \[
        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.
    \]
\end{proposition}

\begin{proof}
    Applying Proposition \ref{proposition:dtn}, we get:
    \begin{align*}
        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k&=\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\sum_{k\in\Z}\kraw{k-\ell}{\w(c)}{n-2t}z^{k-\ell}\\
        &=\left(\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\right)\cdot(1+z)^u\cdot(1-z)^v\\
        &=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.\qedhere
    \end{align*}
\end{proof}

Consequently, we get a generalization of Theorem \ref{theorem:bound_D_nka}:

\begin{theorem}
    Let $t, n\in \N$ with $n$ even and $t\le n/2$. For every $a\in\F_2^n$, it holds that:
    \[
        |\wtk{d_{t,n}}{k}(a)|\leq 2^{n-t/2}.
    \]
\end{theorem}

\begin{proof}
    By applying Property \ref{property:cauchy_estimate}, we get that a bound on $|\wtk{d_{t,n}}{k}(a)|$ is given by the maximum $M'$ on the circle $|z|=1$ of $|P_b(z)|\cdot|(1+z)^u\cdot(1-z)^v|$. As previously established, $|P_b(z)|$ is bounded on $|z|=1$ by $(2\sqrt 2)^t=2^{3t/2}$, and $|(1+z)^u\cdot(1-z)^v|$ is bounded on $|z|=1$ by $2^{u+v}=2^{n-2t}$. Therefore, we conclude that $M'$ is bounded by $2^{3t/2}2^{n-2t}=2^{n-t/2}$, and hence this is also a bound for $|\wtk{d_{t,n}}{k}(a)|$. 
\end{proof}

\begin{Corollary}
    For every $a\in\F_2^n$, the following holds:
    \[
        |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{n-t/2}.
    \]
\end{Corollary}

\begin{proof}
    Analogous to the proof of Corollary \ref{cor:bound_walsh_cauchy}.
\end{proof}
